The Practical Application of Computerised Multistage Tests

### 2021-03-04 article.Rmd
Modified mst-design

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```
This is already showing us something a little weird. Our D (very easy) module is actually a little bit more difficult than our F (moderately hard) module at the top end of the scale. And the E (moderately easy) module is more difficult than the G (very hard) module. All of the modules are quite similar in terms of difficulty (the MCCs are quite close to each other), and moreover the lines are quite flat - there is little discrimination between them. We'll see how this can be expressed more obviously in the next section.

@@

cutScore <- round(df_moduleA_TS$trueScore[which.min(abs(df_moduleA_TS$theta - cutTheta))])
```
Here we can see that there is point of intersection between modules B and C where the ability estimate is `r cutTheta`. If we read off the true score value that is equivalent for this theta estimate in Module A, then we can use this as the cut score; in this case the (rounded) true score is `r cutScore`. Below this value the candidate should be routed to Module B, above it they should be routed to Module C.

![Cut Score](images/cut-score.png)

>>>>

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```
This is already showing us something a little weird. Our E (easy) module is actually a little bit more difficult than our F (hard) module. All of the modules are quite similar in terms of difficulty (the MCCs are quite close to each other), and moreover the lines are quite flat - there is little discrimination between them.

@@

cutScore <- round(df_moduleA_TS$trueScore[which.min(abs(df_moduleA_TS$theta - cutTheta))])
```
Here we can see that there is point of intersection between modules B and C where the ability estimate is `r cutTheta`. If we read off the true score value that is equivalent for this theta estimate in Module A, then we can use this as the cut score; in this case the (rounded) true score is `r cutScore`.
